Pulsar detection - Machine learning and pattern recognition exam

### 2022-07-04 report/paper.tex
Added PCA, LDA and 4 MVG classifiers

Observing the feature pairs it's possible to note that there isn't one that allows to find a clear separation of the two classes. 
\vspace*{0.5cm}
The combination of features represented in graphs (n), (p), (ab), (af) and (ah) get close to identify regions of space where samples are well separated.
\vspace*{0.5cm}\\
The least useful pairs of features are represented in graphs (q), (s), (u) and (ac), where samples are almost entirely overlapping.

% TODO: gaussianize features
% TODO: feature correlation: compute pearson correlation heatmap

\clearpage
\bibliographystyle{unsrt}
\bibliography{citations}

>>>>

Observing the feature pairs it's possible to note that there isn't one that allows to find a clear separation of the two classes.
\vspace*{0.5cm}\\
The combination of features represented in graphs (n), (p), (ab), (af) and (ah) get close to identify regions of space where samples are well separated.
\vspace*{0.5cm}\\
The least useful pairs of features are represented in graphs (q), (s), (u) and (ac), where samples are almost entirely overlapping.
\vspace*{0.5cm}\\
The plots also show that some pair of features share similar distributions, implying that there's a correlation between them.

% TODO: gaussianize features

\clearpage
\subsection{Feature correlation}

Computing the pearson correlation between all pairs of raw features and plotting it as a heatmap we obtain the following result:
\begin{figure}[H]
    \begin{center}
        \subfloat[Pearson correlation heatmap]{\includegraphics[width = 320pt]{img/pearson_correlation/raw_heatmap.png}}
    \end{center}
\end{figure}
The heatmap clearly shows that the following pairs of features are strongly correlated:
\begin{enumerate}
    \item (0) Mean of the integrated profile - (1) Standard deviation of the integrated profile.
    \item (2) Excess kurtosis of the integrated profile - (3) Skewness of the integrated profile.
    \item (4) Mean of the DM-SNR curve - (5) Standard deviation of the DM-SNR curve.
    \item (6) Excess kurtosis of the DM-SNR curve - (7) Skewness of the DM-SNR curve.
\end{enumerate}

While the following pairs of features are weakly correlated, with a pearson coefficient close to 0.4:
\begin{enumerate}
    \item (2) Excess kurtosis of the integrated profile - (4) Mean of the DM-SNR curve
    \item (2) Excess kurtosis of the integrated profile - (5) Standard deviation of the DM-SNR curve
    \item (3) Skewness of the integrated profile - (4) Mean of the DM-SNR curve
    \item (3) Skewness of the integrated profile - (5) Standard deviation of the DM-SNR curve
\end{enumerate}
\clearpage
\bibliographystyle{unsrt}
\bibliography{citations}

% TODO: WHERE TO PUT THIS?
Linear Discriminant Analysis (LDA) is deemed not useful as a preprocessing step for this project as LDA allows to find at most c - 1 discriminant directions, where c is the number of classes, thus we could find at most 1 direction.
